% NOTE:
% "project" should be a custom environment to be used for a single project, internship, etc.
% The specifications of that environment should be as follows:
% First argument is an OPTIONAL link
% Second argument is the name of the project
% Third argument is the date/duration
% Fourth argument is the name of the mentor(s)

\section*{RESEARCH PROJECTS}
\begin{itemize}
\ifsingle{\setlength{\itemsep}{0mm}}

\item \begin{project}{Role of gene bendless in Drosophila hematopoiesis and stem-cell niche}{June '21 -- Oct '21}{Dr.\ Rohan Khadilkar, ACTREC, Navi Mumbai}%chktex 8
    \item Investigated the role of the gene \textbf{Bendless} in Drosophila hematopoiesis and its effect on the stem-cel niche.
    \item Overexpress and knocked out the gene using UAS-GAL4 and RNAi genetic systems and layed out novel data on its effect in the lymph gland and the medullary zone.
    \item Able to \textbf{dissect}, \textbf{immunostain} and \textbf{mount} lymph gland samples.
    \item Mastered the skill of Drosophila larvae micro-dissection requiring extreme precision and care and immunofluroscense. 
    \item Learnt fly husbandry, propagating various genetic fly generations and setting up of genetic crosses.
    \item Handled the Olympus Compact Stereo Microscopes, Zeiss fluroscense microscope and able to analyse the confocal Zeiss LSM 780 images.	
\end{project}

\item \begin{project}{Summer Reading Project, IISER Mohali}{May '21 -- July '21}{Dr.\ Tripta Bhatia}%chktex 8
    \item Studied and presented about the development of multi-celluar organisms specifically about Drosophila Melanogaster.
    \item In-depth studying of the topics from the book 'Molecular Biology Of the Cell' by Bruce Alberts.
    \item Presented the topics through online zoom meetings and discussed about the interesting areas of research that could come up.
\end{project}


\end{itemize}
